---
title: "JTK pval vs q.val"
author: "Andrea Rubio-Ponce"
date: "`r format(Sys.time(), '%m, %Y')`"
output: 
  pdf_document: 
    dev: pdf
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
documentclass: article
urlcolor: blue
classoption: a4paper
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
# Functions, Constants and graphical variables      
knitr::opts_knit$set(root.dir = "/data3/arubio/projects/Andrea_Circadian_benchmark/")
require("knitr")
knitr::opts_chunk$set(
      	fig.align = "center",
      	fig.path = "/data3/arubio/projects/Andrea_Circadian_benchmark/RESULTS/pval_qval/plots/",
      	fig.pos = "H",
      	message = FALSE,
      	warning = FALSE,
      	dev = c("pdf", "png"),
      	dpi = 500,
      	# include = FALSE,
      	root.dir = "/data3/arubio/projects/Andrea_Circadian_benchmark/"
)
setwd("/data3/arubio/projects/Andrea_Circadian_benchmark/")
knitr::opts_knit$get("root.dir")
```


```{r message=FALSE, warning=FALSE, include=FALSE}
library("mouse4302.db")
library("pheatmap")
library("RColorBrewer")
library("affy")
library("limma")
library("tximport")
library("edgeR")
library("sva")
library("RColorBrewer")
library("pheatmap")
library("biomaRt")
library("ggplot2")
library("gplots")
library("NMF")
library("cluster")
library("fpc")
library("plyr")
library("sva")
library("VennDiagram")
library("gProfileR") # GO
library("knitr")
library("xtable")
library("MetaCycle")
library("knitcitations")
library("HarmonicRegression")
library("dplyr")
library("reshape2")
library("AnnotationDbi")
# source("https://bioconductor.org/biocLite.R")

library("affy")
library("readxl")
library("broom")
source("./SRC/Regression_lib.R")
source("./SW/JTKversion3/JTK_CYCLEv3.1.R")


dir.create("./RESULTS/pval_qval/files/", recursive = T)
cite_options(citation_format = "compatibility",
hyperlink = FALSE, cite.style = "authoryear", super = FALSE,
max.names = 1, longnamesfirst = FALSE, check.entries = FALSE)
```

# Description

pvalue vs. qvalue results overview.


```{r message=FALSE, warning=FALSE, include=FALSE}
'%!in%' <- function(x,y)!('%in%'(x,y))
n=11
# hmcol <- colorRampPalette(c("#ce23cb","#000000", "#d6d633"))(n) # pink yellow dim
hmcol <- colorRampPalette(c("#76a5f7","#0c001c", "#ff1d00"))(100) # blue red
# hmcol <- colorRampPalette(c("#FF00FF","#000000","#FFFF00"))(n) # pink yellow seurat
# Color gradient for each timepoint
n=6
colfunc<-colorRampPalette(c("#053061","orange","#67001F"))
time.color <- colfunc(n)
# plot(rep(1,length(hmcol)),col=(colfunc(length(hmcol))), pch=19,cex=2)

# time.colors <- data.frame(row.names = unique(s2c$ZT)
#                          , color = time.color
#                          , stringsAsFactors = F)
```

<!-- # Liver RNAseq -->

<!-- ```{r message=FALSE, warning=FALSE, include=FALSE} -->
<!-- jtk_results <- read.csv("../Ivan_Neutrophils_circadian_Liver/RESULTS/files/jtk_wt_result_liver.csv", row.names = 1) -->
<!-- s2c <- read.csv("../Ivan_Neutrophils_circadian_Liver/DOC/s2c.csv", row.names = 1) -->
<!-- s2c <- s2c[which(s2c$group=="WT"),] -->
<!-- ``` -->


<!-- ```{r message=FALSE, warning=FALSE, include=FALSE} -->
<!-- # Select pval genes -->
<!-- pval <- jtk_results[which(jtk_results$ADJ.P<0.05 & jtk_results$PER>=20 & jtk_results$PER <=30),] -->
<!-- qval <- jtk_results[which(jtk_results$BH.Q<0.05 & jtk_results$PER>=20 & jtk_results$PER <=30),] -->
<!-- pval_list <- as.character(pval$Probeset) -->
<!-- qval_list <- as.character(qval$Probeset) -->
<!-- ``` -->

<!-- ```{r rna_seq_jtk_pval_qval_venn, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5} -->
<!-- intersection <- list(pval_list -->
<!--                      , qval_list -->
<!--                     ) -->
<!-- venn <- venn.diagram( intersection -->
<!--               , filename = NULL -->
<!--               , scale = F -->
<!--               , col = c("red", "blue") -->
<!--               , fill = c("red", "blue") -->
<!--               , alpha = 0.3 -->
<!--               , category.names = c("p-value","BH") -->
<!--               , cat.pos = c(0,0) -->
<!--               , force.unique = TRUE -->
<!--               , margin = 0.0 -->
<!--               , cex = 2 -->
<!--               , cat.cex = 2 -->
<!--               # , ext.text = FALSE -->
<!--               # , main = "NLS detected genes" -->
<!--               # , main.fontface = "bold" -->
<!-- ) -->

<!-- grid.draw(venn) -->
<!-- ``` -->

<!-- ```{r, message=FALSE, warning=FALSE, include=FALSE} -->
<!-- # Clean up after stupid venndiagram -->
<!-- do.call(file.remove, list(list.files(path = "./RESULTS/pval_qval/plots/", pattern = "*.log", full.names = TRUE))) -->
<!-- do.call(file.remove, list(list.files(path = "./", pattern = "*.log", full.names = TRUE))) -->
<!-- ``` -->


<!-- ```{r message=FALSE, warning=FALSE, include=FALSE} -->
<!-- pval_only <- pval_list[which(pval_list %!in% qval_list)] -->
<!-- ``` -->

<!-- ```{r rna_seq_hm_pval_only, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- col.annotation <- data.frame(row.names = s2c$sample, time = s2c$ZT) -->

<!-- # Plot -->
<!-- pheatmap(  as.matrix(jtk_results[pval_only,as.character(s2c$sample)]) -->
<!--          , scale = "row" -->
<!--          , color = hmcol -->
<!--          , border_color = "NA" -->
<!--          , cellwidth = 5 -->
<!--          , cluster_rows = T -->
<!--          , cluster_cols = F -->
<!--          , treeheight_row = 0 -->
<!--          , treeheight_col = 15 -->
<!--          , annotation_col = col.annotation -->
<!--          , legend = T -->
<!--          , show_rownames = F -->
<!--          , show_colnames = F -->
<!--          , display_numbers = F -->
<!--          , annotation_names_row = F -->
<!--          , annotation_names_col = F -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r rna_seq_hm_qval_only, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- col.annotation <- data.frame(row.names = s2c$sample, time = s2c$ZT) -->

<!-- # Plot -->
<!-- pheatmap(  as.matrix(jtk_results[qval_list,as.character(s2c$sample)]) -->
<!--          , scale = "row" -->
<!--          , color = hmcol -->
<!--          , border_color = "NA" -->
<!--          , cellwidth = 5 -->
<!--          , cluster_rows = T -->
<!--          , cluster_cols = F -->
<!--          , treeheight_row = 0 -->
<!--          , treeheight_col = 15 -->
<!--          , annotation_col = col.annotation -->
<!--          , legend = T -->
<!--          , show_rownames = F -->
<!--          , show_colnames = F -->
<!--          , display_numbers = F -->
<!--          , annotation_names_row = F -->
<!--          , annotation_names_col = F -->
<!-- ) -->
<!-- ``` -->

# Results
## In silico data

```{r message=FALSE, warning=FALSE, include=FALSE}
jtk_results <- read.csv("./RESULTS/Subsampling/files/subsampling_JTK_24_4_3_reps.csv", row.names = 1)
# Generate s2c
times <- colnames_array <- grep("rep", colnames(jtk_results), value=T)
colnames(jtk_results) <- gsub("_", "", colnames(jtk_results))
colnames_array <- grep("rep", colnames(jtk_results), value=T)
s2c <- data.frame(sample=colnames_array
                 , ZT=gsub("[S\\_]", "", sapply(strsplit(times, "rep|\\."), "[[", 1))
                 , ind=rep(c(1:3),length.out=length(colnames_array))
                 , stringsAsFactors = F
)

# Get tp and fp
full_exprs <- read.csv("./RAW/Subsampling/subsampling_in_silico_data.csv", row.names=1)
# For per 20:30 (circadian)
real_c_genes <- full_exprs[which(full_exprs$per>=20 & full_exprs$per <=30),]
real_c_negat <- full_exprs[which(rownames(full_exprs) %!in% rownames(real_c_genes)),]
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Select pval genes
pval <- jtk_results[which(jtk_results$ADJ.P < 0.05 & jtk_results$PER>=20 & jtk_results$PER <=30),]
qval <- jtk_results[which(jtk_results$BH.Q<0.05 & jtk_results$PER>=20 & jtk_results$PER <=30),]
pval_list <- as.character(pval$Probeset)
qval_list <- as.character(qval$Probeset)
```

```{r in_silico_jtk_pval_qval_venn, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3, fig.height=3}
intersection <- list(pval_list
                     , qval_list
                    )
venn <- venn.diagram( intersection
              , filename = NULL
              , scale = T
              , col = c("red", "blue")
              , fill = c("red", "blue")
              , alpha = 0.3
              , category.names = c("p-value","BH")
              , cat.pos = c(0,0)
              , force.unique = TRUE
              , margin = 0.0
              , cex = 2
              , cat.cex = 2
)

grid.draw(venn)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Clean up after stupid venndiagram
do.call(file.remove, list(list.files(path = "./RESULTS/pval_qval/plots/", pattern = "*.log", full.names = TRUE)))
do.call(file.remove, list(list.files(path = "./", pattern = "*.log", full.names = TRUE)))
```

Plot all genes obtained with p-value, separated by true and false positives.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Classify genes in tp or fp
all_results <- jtk_results[pval_list,]
all_results[pval_list[which(pval_list %in% rownames(real_c_genes))],"class_pval"] <- "tp"
all_results[pval_list[which(pval_list %!in% rownames(real_c_genes))],"class_pval"] <- "fp"
```


```{r message=FALSE, warning=FALSE, include=FALSE}
col.annotation <- data.frame(row.names = s2c$sample, time = s2c$ZT)
# Row annotation
row.annotation <- data.frame(row.names = all_results$Probeset, class=all_results$class_pval)
# Define colors for each category
map.colors <- list(time = setNames(time.color, unique(s2c$ZT))
                  , class = c(tp = "deepskyblue3"
                            , fp = "firebrick4")
)
# Subset to plot
m <- all_results
# Get the order of the clustered rows
temp <- m[which(m$class_pval=="tp"),]
ph.tp <- pheatmap(as.matrix(temp[,as.character(s2c$sample)]), cluster_rows=TRUE)$tree_row$order
ph.tp <- temp[ph.tp,"Probeset"]
temp <- m[which(m$class_pval=="fp"),]
ph.fp <- pheatmap(as.matrix(temp[,as.character(s2c$sample)]), cluster_rows=TRUE)$tree_row$order
ph.fp <- temp[ph.fp,"Probeset"]
# Sort matrix
m <- m[as.character(c(ph.fp, ph.tp)),]
```

From all the significant genes when using p-value<0.05 , `r length(ph.tp)` were TP (`r length(ph.tp)/(length(ph.tp)+length(ph.fp))*100`%) and `r length(ph.fp)` were FP (`r length(ph.fp)/(length(ph.tp)+length(ph.fp))*100`%).

```{r in_silico_hm_pval_all, echo=FALSE, message=FALSE, warning=FALSE}
# Plot
pheatmap(  as.matrix(m[,as.character(s2c$sample)])
         , scale = "row"
         , color = hmcol
         , border_color = "NA"
         , cellwidth = 5
         , cluster_rows = F
         , cluster_cols = F
         , treeheight_row = 0
         , treeheight_col = 0
         , annotation_row = row.annotation
         , annotation_col = col.annotation
         , annotation_colors = map.colors
         , gaps_row = length(ph.fp)
         , legend = T
         , show_rownames = F
         , show_colnames = F
         , display_numbers = F
         , annotation_names_row = F
         , annotation_names_col = F
)
```

```{r fp_tp_all_bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=2, fig.height=4}
count <- t(rbind(pval=table(all_results$class_pval)))
count <- melt(count)

ggplot(count, aes(y = value, x = Var2, fill = Var1))+
  geom_bar(stat = "identity",color="white")+
  scale_fill_manual(name = "Total hits"
                   , values = c("firebrick4", "deepskyblue3")
                   # , labels = c("False Positives", "True Positives")
                   ) +
  ylab("Gene #") +
  xlab("Filtering method") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)
      , panel.background = element_blank())
```

```{r message=FALSE, warning=FALSE, include=FALSE}
pval_only <- pval_list[which(pval_list %!in% qval_list)]
jtk_results[pval_only[which(pval_only %in% rownames(real_c_genes))],"class_pval"] <- "tp"
jtk_results[pval_only[which(pval_only %!in% rownames(real_c_genes))],"class_pval"] <- "fp"
jtk_results[qval_list[which(qval_list %in% rownames(real_c_genes))],"class_qval"] <- "tp"
jtk_results[qval_list[which(qval_list %!in% rownames(real_c_genes))],"class_qval"] <- "fp"

jtk_results[as.character(pval$Probeset[which(pval$Probeset %in% rownames(real_c_genes))]),"class_both"] <- "tp"
jtk_results[as.character(pval$Probeset[which(pval$Probeset %!in% rownames(real_c_genes))]),"class_both"] <- "fp"
```

```{r message=FALSE, warning=FALSE, include=FALSE}
col.annotation <- data.frame(row.names = s2c$sample, time = s2c$ZT)
# Row annotation
row.annotation <- data.frame(row.names = jtk_results$Probeset, class=jtk_results$class_pval)
# Define colors for each category
map.colors <- list(time = setNames(time.color, unique(s2c$ZT))
                  , class = c(tp = "deepskyblue3"
                            , fp = "firebrick4")
)
# Subset to plot
m <- jtk_results[pval_only,]
# Get the order of the clustered rows
temp <- m[which(m$class_pval=="tp"),]
ph.tp <- pheatmap(as.matrix(temp[,as.character(s2c$sample)]), cluster_rows=TRUE)$tree_row$order
ph.tp <- temp[ph.tp,"Probeset"]
temp <- m[which(m$class_pval=="fp"),]
ph.fp <- pheatmap(as.matrix(temp[,as.character(s2c$sample)]), cluster_rows=TRUE)$tree_row$order
ph.fp <- temp[ph.fp,"Probeset"]
# Sort matrix
m <- m[as.character(c(ph.fp, ph.tp)),]
```

From the p-value only fraction, `r length(ph.tp)` were TP (`r length(ph.tp)/(length(ph.tp)+length(ph.fp))*100`%) and `r length(ph.fp)` were FP (`r length(ph.fp)/(length(ph.tp)+length(ph.fp))*100`%).

```{r in_silico_hm_pval_only, echo=FALSE, message=FALSE, warning=FALSE}
# Plot
pheatmap(  as.matrix(m[,as.character(s2c$sample)])
         , scale = "row"
         , color = hmcol
         , border_color = "NA"
         , cellwidth = 5
         , cluster_rows = F
         , cluster_cols = F
         , treeheight_row = 0
         , treeheight_col = 0
         , annotation_row = row.annotation
         , annotation_col = col.annotation
         , annotation_colors = map.colors
         , gaps_row = length(ph.fp)
         , legend = T
         , show_rownames = F
         , show_colnames = F
         , display_numbers = F
         , annotation_names_row = F
         , annotation_names_col = F
)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# Row annotation
row.annotation <- data.frame(row.names = jtk_results$Probeset, class=jtk_results$class_qval)
# Define colors for each category
# Subset to plot
m <- jtk_results[qval_list,]
# Get the order of the clustered rows
temp <- m[which(m$class_qval=="tp"),]
ph.tp <- pheatmap(as.matrix(temp[,as.character(s2c$sample)]), cluster_rows=TRUE)$tree_row$order
ph.tp <- temp[ph.tp,"Probeset"]
temp <- m[which(m$class_qval=="fp"),]
ph.fp <- pheatmap(as.matrix(temp[,as.character(s2c$sample)]), cluster_rows=TRUE)$tree_row$order
ph.fp <- temp[ph.fp,"Probeset"]
# Sort matrix
m <- m[as.character(c(ph.fp, ph.tp)),]
```

From the q-value only fraction, `r length(ph.tp)` were TP (`r length(ph.tp)/(length(ph.tp)+length(ph.fp))*100`%) and `r length(ph.fp)` were FP (`r length(ph.fp)/(length(ph.tp)+length(ph.fp))*100`%).

```{r in_silico_hm_qval_only, echo=FALSE, message=FALSE, warning=FALSE}
# Plot
pheatmap(  as.matrix(m[,as.character(s2c$sample)])
         , scale = "row"
         , color = hmcol
         , border_color = "NA"
         , cellwidth = 5
         , cluster_rows = F
         , cluster_cols = F
         , treeheight_row = 0
         , treeheight_col = 0
         , annotation_row = row.annotation
         , annotation_col = col.annotation
         , annotation_colors = map.colors
         , gaps_row = length(ph.fp)
         , legend = T
         , show_rownames = F
         , show_colnames = F
         , display_numbers = F
         , annotation_names_row = F
         , annotation_names_col = F
)
```

```{r fp_tp_bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3}
count <- t(rbind(pval=table(jtk_results[as.character(pval$Probeset),]$class_both)
             , qval=table(jtk_results[as.character(qval$Probeset),]$class_both)))
count <- melt(count)

ggplot(count, aes(y = value, x = Var2, fill = Var1))+
  geom_bar(stat = "identity",color="white")+
  scale_fill_manual(name = "Total hits"
                   , values = c("firebrick4", "deepskyblue3")
                   # , labels = c("False Positives", "True Positives")
                   ) +
  ylab("Gene #") +
  xlab("Filtering method") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)
        , panel.background = element_blank())
```

```{r fp_tp_bars_pval, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3, fig.height=4}
count <- t(rbind(pval=table(jtk_results[as.character(pval_only),]$class_both)))
count <- melt(count)

ggplot(count, aes(y = value, x = Var2, fill = Var1))+
  geom_bar(stat = "identity",color="white")+
  scale_fill_manual(name = "Total hits"
                   , values = c("firebrick4", "deepskyblue3")
                   # , labels = c("False Positives", "True Positives")
                   ) +
  ylab("Gene #") +
  xlab("Filtering method") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)
        , panel.background = element_blank())
```

```{r fp_tp_bars_qval, echo=FALSE, message=FALSE, warning=FALSE, fig.width=3, fig.height=4}
count <- t(rbind(qval=table(jtk_results[as.character(qval$Probeset),]$class_both)))
count <- melt(count)

ggplot(count, aes(y = value, x = Var2, fill = Var1))+
  geom_bar(stat = "identity",color="white")+
  scale_fill_manual(name = "Total hits"
                   , values = c("firebrick4", "deepskyblue3")
                   # , labels = c("False Positives", "True Positives")
                   ) +
  ylab("Gene #") +
  xlab("Filtering method") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)
        , panel.background = element_blank())
```



# References

```{r bibliography, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
bibliography()
```
