---
title: "Benchmarking of subsampled datasets ROC curves using JTK and NLS."
author: "Andrea Rubio-Ponce"
date: "`r format(Sys.time(), '%m, %Y')`"
output: 
  pdf_document: 
    dev: pdf
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
documentclass: article
urlcolor: blue
classoption: a4paper
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
- \usepackage{longtable}
---


```{r setup, message=FALSE, warning=FALSE, include=FALSE}
# Functions, Constants and graphical variables      
knitr::opts_knit$set(root.dir = "/data3/arubio/projects/Andrea_Circadian_benchmark/")
require("knitr")
knitr::opts_chunk$set(
    	fig.align = "center",
    	fig.path = "/data3/arubio/projects/Andrea_Circadian_benchmark/RESULTS/Subsampling/plots/",
    	fig.pos = "H",
    	message = FALSE,
    	warning = FALSE,
    	dev = c("png", "pdf"),
    	dpi = 500,
    	# include = FALSE,
    	root.dir = "/data3/arubio/projects/Andrea_Circadian_benchmark/"
      )
setwd("/data3/arubio/projects/Andrea_Circadian_benchmark/")
knitr::opts_knit$get("root.dir")
```


```{r, message=FALSE, warning=FALSE, include=FALSE}
library("RColorBrewer")
library("pheatmap")
library("ggplot2")
library("gplots")
library("NMF")
library("cluster")
library("fpc")
library("plyr")
library("VennDiagram")
library("knitr")
library("xtable")
library("knitcitations")
library("dplyr")
library("reshape2")
library("AnnotationDbi")
library("mouse4302.db")
library("affy")
library("broom")
library("nlme")
library("panp")
library("MetaCycle")
library("cowplot")
source("./SW/JTKversion3/JTK_CYCLEv3.1.R")
source("./SRC/Regression_lib.R")
source("./SRC/Utils.R")

# dir.create("./RESULTS/NLS_benchmarking/Hughes/files/", recursive = T)
dir.create("./RESULTS/Subsampling/files/", recursive=T)
dir.create("./RAW/Subsampling/", recursive=T)
cite_options(citation_format = "compatibility",
hyperlink = FALSE, cite.style = "authoryear", super = FALSE,
max.names = 1, longnamesfirst = FALSE, check.entries = FALSE)
```


# Description

We create a single dataframe of 48x1 in silico. An 80% of the genes are generated using the madsim package `r sanitize(citep(citation("madsim")))`. The other 20% were generated using random periods (8:30), amplitudes (0.5:4) and phases (-6:6) and adding normal noise and a SD = 1.5.
With that dataframe, different subsamling is done to recreate several experiment configurations.
Number of replicates: 1, 3 and 5
Experimental design: 24h and 48h long with 1,2,3,4, and 6h between timepoints.
To see how well every algorithm does with different frequencies and amplitudes, the genes considered "true" were divided into categories:
All rythmic genes: all amps, per 8:30
Ultradian genes: all amps, per 8:19
Circadian genes: all amps, per 20:30
Low genes: amp 0:1.5, all pers
High genes: amp 1.5: , all pers

A gene is considered "positive" if it passes the threshold of significance and the estimated period or amplitude is in the range of the true gene (per = 8:19 for ultradian genes and so on).

This is an appendix of the subsampling code to generate al the ROC curves of NLS and JTK.

## ROC Curves

```{r message=FALSE, warning=FALSE, include=FALSE}
if(!file.exists("./RESULTS/Subsampling/files/roc_results.csv")){
  roc.data <- setNames(data.frame(matrix(ncol = 8, nrow = 0))
                     , c("Dataset","Algorithm", "threshold", "Reps","TP", "FP", "FN", "TN"))
  algorithms <- c("JTK", "NLS")
  sequence <- round(seq(from = 0, to = 1, length.out = 1000),digits=3)
  for (nreps in reps){
    for (l in lengths){
      for (s in sampling){
        for (a in algorithms){
            full_exprs <- read.csv("./RAW/Subsampling/subsampling_in_silico_data.csv", row.names=1)
            # Get real genes
            real_genes <- full_exprs[which(!is.na(full_exprs$per)),]
            real_negat <- full_exprs[which(is.na(full_exprs$per)),]
            a_results <- read.csv(paste("./RESULTS/Subsampling/files/subsampling_",a,"_",l,"_",s,"_", nreps,"_reps.csv", sep=""))
            cat(nreps,l,s,a,"\n")
            for (i in sequence){
              if(a=="JTK"){
                results_roc <- a_results[which(jtk_results$BH.Q<0.05 & a_results$PER>=20 & a_results$PER<=30),]
                detected <- results_roc$Probeset
              }else{
                results_roc <- a_results[which(a_results$estimate.per<=30 &
                                            a_results$estimate.per>=20 &
                                           (a_results$BH.q.value.per<0.05 | is.na(a_results$BH.q.value.per)) &
                                            a_results$r>=0.7 &
                                            a_results$BH.q.value.amp<0.05
                                           ),]
                detected <- results_roc$feature
              }
                tp <-  Reduce(intersect, list(rownames(real_genes),detected))
                fp <- detected[detected %!in% rownames(real_genes)]
                fn <- rownames(real_genes)[rownames(real_genes) %!in% detected]
                tn <- rownames(real_negat)[rownames(real_negat) %!in% detected]
                
                df <- data.frame(rbind(tp=length(tp), fp=length(fp),fn=length(fn), tn=length(tn)))
                df$group <- rownames(df)
                colnames(df) <- c("value", "group")
                df$group <-  factor(df$group, levels = c("fn", "fp", "tp", "tn"))
                # Store the results
                roc.data[nrow(roc.data)+1,] <-  c(paste(l,s,sep="x")
                                                  , a
                                                  , i
                                                  , nreps
                                                  , as.numeric(length(tp))
                                                  , as.numeric(length(fp))
                                                  , as.numeric(length(fn))
                                                  , as.numeric(length(tn))
                )
            }
        }
      }
    }
  }
  write.csv(roc.data, "./RESULTS/Subsampling/files/roc_results.csv")
}else{
  roc.data <- read.csv("./RESULTS/Subsampling/files/roc_results.csv")
  
}
roc.data$Reps <- as.character(roc.data$Reps)
roc.data$s <- paste("x ", roc.data$s, "h", sep="")
```


```{r nls_jtk_roc_curves, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
roc_data_subset <- subset(roc.data[which(roc.data$Algorithm=="NLS" & roc.data$l==24),], select=-c(Algorithm))
roc_data_subset$Reps <- as.character(roc_data_subset$Reps)
nls_plot <- ggplot(roc_data_subset,aes(y = tpr, x = fpr, color = Reps))+
              geom_line() +
              # xlim(0,0.20) +
              ylim(0,1) +
              labs(color = "Replicate #") + 
              ggtitle("NLS") +
              facet_wrap(~s,ncol=1
                         , scales="free" # Keep the axis on all the plots
                         ) +
              theme(axis.title=element_blank()
                  , axis.ticks=element_blank()
                  , strip.background = element_rect(colour="white", fill="white")
                  , strip.placement = "outside"
                  , strip.text = element_text(size=10, face="bold")
                  , axis.text = element_text(size=8)
                  , strip.text.y = element_text(hjust=-10)
              )

roc_data_subset <- subset(roc.data[which(roc.data$Algorithm=="JTK" & roc.data$l==24),], select=-c(Algorithm))

jtk_plot <- ggplot(roc_data_subset,aes(y = tpr, x = fpr, color = Reps))+
              geom_line() +
              # xlim(0,0.20) +
              ylim(0,1) +
              labs(color = "Replicate #") + 
              ggtitle("JTK") +
              facet_wrap(~s,ncol=1
                         , scales='free'
                         ) +
              theme(axis.title=element_blank()
                  , axis.ticks=element_blank()
                  , strip.background = element_rect(colour="white", fill="white")
                  , strip.placement = "outside"
                  , strip.text = element_text(size=10, face="bold")
                  , axis.text = element_text(size=8)
                  , strip.text.y = element_text(hjust=-10)
              )

plot_grid(nls_plot,jtk_plot)
```

```{r nls_jtk_roc_curves_xlim_0_20, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
roc_data_subset <- subset(roc.data[which(roc.data$Algorithm=="NLS" & roc.data$l==24),], select=-c(Algorithm))
roc_data_subset$Reps <- as.character(roc_data_subset$Reps)
nls_plot <- ggplot(roc_data_subset,aes(y = tpr, x = fpr, color = Reps))+
              geom_line() +
              xlim(0,0.10) +
              ylim(0,1) +
              labs(color = "Replicate #") + 
              ggtitle("NLS") +
              facet_wrap(~s,ncol=1
                         , scales="free" # Keep the axis on all the plots
                         ) +
              theme(axis.title=element_blank()
                  , axis.ticks=element_blank()
                  , strip.background = element_rect(colour="white", fill="white")
                  , strip.placement = "outside"
                  , strip.text = element_text(size=10, face="bold")
                  , axis.text = element_text(size=8)
                  , strip.text.y = element_text(hjust=-10)
              )

roc_data_subset <- subset(roc.data[which(roc.data$Algorithm=="JTK" & roc.data$l==24),], select=-c(Algorithm))

jtk_plot <- ggplot(roc_data_subset,aes(y = tpr, x = fpr, color = Reps))+
              geom_line() +
              xlim(0,0.10) +
              ylim(0,1) +
              labs(color = "Replicate #") + 
              ggtitle("JTK") +
              facet_wrap(~s,ncol=1
                         , scales='free'
                         ) +
              theme(axis.title=element_blank()
                  , axis.ticks=element_blank()
                  , strip.background = element_rect(colour="white", fill="white")
                  , strip.placement = "outside"
                  , strip.text = element_text(size=10, face="bold")
                  , axis.text = element_text(size=8)
                  , strip.text.y = element_text(hjust=-10)
              )

plot_grid(nls_plot,jtk_plot)
```
